\Title

### 2021-01-08 manuscript/manuscript.tex
Minor changes
Apply suggestions from code review
Co-authored-by: Leonardo Uieda <leouieda@gmail.com>

\begin{enumerate}
  \item
    \emph{Constant depth}:
    The simplest option is to locate all sources at the same depth
    (Fig.~\ref{fig:depth_types}a).
If the measurement were taken at significantly different altitudes, the
elevated computation points will be more distant to the sources than the lower
ones.
This may create problems on reproducing high frequencies on the elevated
points.
 \item
    \emph{Relative depth}:
One possible solution is to locate each source below its corresponding
observation (or block averaged) point at a constant \emph{relative depth}
from it.
The depth of each source can be computed as the height of its corresponding
observation (or block averaged) point minus a depth parameter that assumes the
same value for all sources (see Fig.~\ref{fig:depth_types}(b)).
The sources won't be all at the same depth, but they will all be at the same
distance from their corresponding observation (or block averaged) point.
 \item
    \emph{Variable depth}:
In case our survey presents heavily clustered data points on some areas, we may
want the sources below that region to be shallower in order to reproduce the
high frequencies measured by these clustered observation points.
We can propose a \emph{variable depth} approach: it locates each point source
according to the \emph{relative depth} and then subtracts a term proportional
to the mean distance to its $k$ nearest neighbour sources
(see Fig.~\ref{fig:depth_types}(c)).

So, the depth of the sources can be computed as follows:

\begin{equation}
    \begin{split}
        \textrm{depth} =
           &\textrm{data point height} - \textrm{relative depth} \\
           &- \textrm{depth factor} \cdot \textrm{mean distance}
    \end{split}
\end{equation}

\noindent where \emph{data point height} is the elevation of the corresponding
observation (or block averaged) point, \emph{mean distance} is the mean
distance to the $k$ nearest source neighbours, \emph{depth factor} and
\emph{relative depth} are parameters.
The addition of this new term will make clustered sources to be shallower than
scattered and distant sources.

Similar approaches for setting sources at depths that depend
on the distance to their nearest neighbours were already proposed by
\citet{cordell1992, guspi2004, guspi2009}.
\end{enumerate}

We will test each of these strategies on synthetic data to evaluate their
effectiveness.

@@

\begin{table*}
    \centering
    \caption{
        Source distributions as combinations of source layouts and depth
        strategies.
    }
    \label{tab:source-distributions}
    \begin{tabular}{lccc}
        & Source below data & Block averaged sources & Grid sources \\ \hline
        Constant depth & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
        Relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
        Variable depth & $\checkmark$ & $\checkmark$ & $\times$     \\
    \end{tabular}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\begin{enumerate}
  \item
    \emph{Constant depth}:
    The simplest option is to locate all sources at the same depth
    (Fig.~\ref{fig:depth_types}a).
    If the measurements were taken at significantly different altitudes, some
    measurements will be more distant to the sources than others,
    which may create problems for reproducing short wavelengths in high
    altitude points.
 \item
    \emph{Relative depth}:
    The depths of sources are determined by shifting the vertical coordinate of
    data points downward by a fixed amount (Fig.~\ref{fig:depth_types}b).
    The sources will not all be at the same vertical coordinate, but they will
    all be at the same vertical distance from the observation points.
 \item
    \emph{Variable depth}:
    The depths of sources are proportional to the horizontal distance to the
    nearest neighbouring data points or sources (Fig.~\ref{fig:depth_types}c).
    Different variations of this strategy have been proposed before, for
    example \citet{cordell1992}, \citet{guspi2004}, and \citet{guspi2009}.
    The rationale for this strategy is that if a survey has data points
    clustered in some areas, we may
    want the sources below those areas to be shallower in order to preserve the
    shorter wavelengths that can be measured.
\end{enumerate}

Our approach to the \emph{variable depth} strategy will be:

\begin{equation}
  z = z_{obs} + \Delta z + \alpha h,
\end{equation}

\noindent
in which $z$ is the depth of an equivalent source,
$\Delta z$ is a relative depth shift that is the same for all sources,
$\alpha$ is an adimensional depth factor,
$h$ is the median horizontal distance to the $k$ nearest neighbouring sources,
and
$z_{obs}$ is a vertical observation coordinate that will depend on the
horizontal layout strategy.
For \emph{sources-below-data}, it is the vertical coordinate of the data point
corresponding to the given source.
For \emph{regular-grid}, it can be interpolated from the vertical coordinates
of all data points.
Finally, for \emph{block-averaged-sources} it will be the average vertical
coordinate of data within the corresponding block.

In the following sections, we will test the effectiveness and trade-offs of
each of these strategies on synthetic data.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{table*}
    \centering
    \caption{
        Source distributions as combinations of source layouts and depth
        strategies.
    }
    \label{tab:source-distributions}
    \begin{tabular}{lccc}
        & Source below data & Block averaged sources & Grid sources \\ \hline
        Constant depth & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
        Relative depth & $\checkmark$ & $\checkmark$ & $\times$     \\
        Variable depth & $\checkmark$ & $\checkmark$ & $\times$     \\
    \end{tabular}
\end{table*}
